Correctness of Algebraic File Synchronization

### 2015-11-24 2015/paper.tex
Finalizing text

\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
\newcommand{\recb}{\recchar{B}{A}{}}
\newcommand{\recaset}{\recchar{A}{B}{*}}
\newcommand{\recbset}{\recchar{B}{A}{*}}

@@

\section{Ordering commands}

@@

@@

% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

@@

TODO: we'll treat sequences as sets and sets as sequences
once we know they can be applied.

\begin{mylem}\label{lemma:neighbor}
If $U$ contains commands on both $n$ and $\parent(n)$, then
there is a $U'\in\orderset{U}$ where they are next to each other.
\end{mylem}

@@

\begin{mydef}{Independent commands, sequences and sets.}
For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
% TODO use w() instead of nequiv break
For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
\end{mydef}

@@

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = \ordered{A\setminus B}$ and $\recb = \ordered{B\setminus A}$.
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca = \ordered{\recaset}$  where $\recaset \subset A\setminus B$
and $\recb = \ordered{\recbset}$ where $\recbset \subset B\setminus A$ 
so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any command left out from $\reca$ or $\recb$ will break the filesystems.

We assume that $A$ and $B$ are returned by an update detector,
and so they are simple sequences.
We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $\works{A,B}$.

Our reconciliation algorithm is as follows.

\begin{mydef}{Reconciliation}\label{def:reconciliation}
\begin{align*}
\recaset = \{c| & \\
& c\in A\setminus B \\
& \wedge \\
& \forall c'\in B\setminus A: c\indep c'\\
\} & \\
\reca = \ordered{\recaset}&
\end{align*}

In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
that independent from every command in $B\setminus A$.
\end{mydef}

>>>>

\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
\newcommand{\recb}{\recchar{B}{A}{}}

@@

\section{Ordering commands}\label{ordering}

@@

It follows from the algorithm that:
\begin{mylem}\label{lemma:neighbor}
If $U$ contains commands on both $n$ and $\parent(n)$, then
there is a $U'\in\orderset{U}$ where they are next to each other.
\end{mylem}

@@

@@

It follows from this that given a simple set,
we can simply assume that it has an order.
Accordingly, we will at times treat not only sequences as sets,
but simple sets as sequences.

We work based on the assumption that to achieve this, we need
to apply to $\FS_B$ the commands that have been applied to $\FS_A$, and \emph{vice versa}.
As some commands may have been applied to both filesystems, our first approximation
is $\reca = A\setminus B$ and $\recb = B\setminus A$
(in some suitable order).
This, however, will break both filesystems if there have been incompatible updates
in $A$ and $B$. 
Our aim is therefore to provide an algorithm that selects the commands 
$\reca \subset A\setminus B$
and $\recb \subset B\setminus A$ 
so that $\reca\FS_B\neq\fsbroken$ and $\recb\FS_A\neq\fsbroken$,
and show that these are the longest sequences with this property, that is,
adding any command left out from $\reca$ or $\recb$ will break the filesystems.

We assume that $A$ and $B$ are returned by an update detector,
and so they are simple sequences.
(Otherwise, they can be simplified to become simple sequences.)
We also assume that $\FS_A$ and $\FS_B$ are not broken.
With these assumptions,
we can now define independent sequences and
our reconciliation algorithm.

\begin{mydef}{Independent commands, sequences and sets.}
For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
\end{mydef}

\begin{mydef}{Reconciliation}\label{def:reconciliation}
\begin{align*}
\reca = \{c| & \\
& c\in A\setminus B \\
& \wedge \\
& \forall c'\in B\setminus A: c\indep c'\\
\} &
\end{align*}

In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
that are independent of every command in $B\setminus A$.
The order of commands in the sequence can be determined using the algorithm described in
\cref{ordering} as any subset of $A$ is also simple.
\end{mydef}

% 'Works'
% -------

@@

@@
